The perceptual dimensions of \\ sonority-driven epenthesis

### 2013-10-07 paper.tex
Changed display of CCCC data

\citet{rose.2000} reformulates this as a violable, but categorical, constraint within the context of Optimality Theory and uses it in an analysis of Chaha sonority-driven epenthesis:

\ex.  \textsc{SyllCon}: The first segment of the onset of a syllable must be lower in sonority than the last segment in the immediately preceding syllable.

@@

\ex. \a. {\sc SyllCon}: The first segment of the onset of a syllable must be lower in sonority 
     \b. {\sc SyllCon(Loose}): The first segment of the onset of a syllable must not be of greater sonority than the last segment of the immediately preceding syllable.

@@

In this section, I will demonstrate that the four rankings already obtained in $\S$\ref{CCCanalysis} for the triconsonantal clusters predict almost exactly which of the quadriconsonantal clusters should display variation, and in which direction.

@@

\begin{center}
\begin{tabular}{|cc|c|} \hline
   & Underlying form & Observed surface forms \\ \hline
 a.& \textipa{sdBn} & \textipa{sd1Bn} \\ 
 b.& \textipa{wzfn} & \textipa{wz1fn}, \textipa{w1zf1n} \\
 c.& \textipa{gdfn} & \textipa{gd1fn}, \textipa{g1df1n} \\
 d.& \textipa{mstn} & \textipa{m1st1n} \\
 e.& \textipa{dmdn} & \textipa{d1md1n} \\
 f.& \textipa{drsn} & \textipa{d1rs1n} \\
 g.& \textipa{sBxn} & \textipa{s1Bx1n} \\
 h.& \textipa{kftn} & \textipa{k1ft1n}  \\
 i.& \textipa{ktfn} & \textipa{kt1fn}, \textipa{k1tf1n} \\
 j.& \textipa{sgdn} & \textipa{sg1dn}, \textipa{s1gd1n} \\
 k.& \textipa{srBn} & \textipa{sr1Bn}, \textipa{s1rB1n} \\
 l.& \textipa{krmn} & \textipa{kr1mn}, \textipa{k1rm1n}  \\ \hline
 \end{tabular}
\end{center}

@@

\begin{center} \renewcommand*\arraystretch{1.2}
\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c:c|} \hline 
\multicolumn{3}{|c||}{Input:~/\textipa{n-\textnormal{CCC}-n@}/} & Align-Left & Anchor-Left Root \\[0.5ex]
\hline \hline a. & & \textipa{n1\textnormal{C.C}1\textnormal{C}.n@} & 2,3,5,6 & $\ast$! \\
\hline b. & \ding{43} & \textipa{n1.\textnormal{C}1\textnormal{C.C}1.n@} & 2,4!,5,7 & \\
\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}

>>>>

\cite{rose.2000} reformulates this as a violable, but categorical, constraint within the context of Optimality Theory and uses it in an analysis of Chaha sonority-driven epenthesis:

\ex.  \textsc{SyllCon}: The first segment of the onset of a syllable must be lower in sonority than the last segment in the immediately preceding syllable. \citep[(5)]{rose.2000}

@@

\ex. \a. {\sc SyllCon}: The first segment of the onset of a syllable must be lower in sonority  \citep[(5)]{rose.2000}
     \b. {\sc SyllCon(Loose}): The first segment of the onset of a syllable must not be of greater sonority than the last segment of the immediately preceding syllable. \citep[(49)]{rose.2000}

@@

In this section, I will demonstrate that the four rankings already obtained in $\S$\ref{CCCanalysis} for the triconsonantal clusters generalise without modification to the CCCC clusters, predicting almost exactly which of the quadriconsonantal clusters should display variation, and in which direction.

@@

\begin{center}
\begin{tabular}{|cc|c|} \hline
   & Underlying form & Observed surface forms \\ \hline
 a.& \textipa{n-sdB-n@} & \textipa{n1sd1Bn@} \\ 
 b.& \textipa{n-wzf-n@} & \textipa{n1wz1fn@}, \textipa{n1w1zf1n@} \\
 c.& \textipa{n-gdf-n@} & \textipa{n1gd1fn@}, \textipa{n1g1df1n@} \\
 d.& \textipa{n-mst-n@} & \textipa{n1m1st1n@} \\
 e.& \textipa{n-dmd-n@} & \textipa{n1d1md1n@} \\
 f.& \textipa{n-drs-n@} & \textipa{n1d1rs1n@} \\
 g.& \textipa{n-sBx-n@} & \textipa{n1s1Bx1n@} \\
 h.& \textipa{n-kft-n@} & \textipa{n1k1ft1n@}  \\
 i.& \textipa{n-ktf-n@} & \textipa{n1kt1fn@}, \textipa{n1k1tf1n@} \\
 j.& \textipa{n-sgd-n@} & \textipa{n1sg1dn@}, \textipa{n1s1gd1n@} \\
 k.& \textipa{n-srB-n@} & \textipa{n1sr1Bn@}, \textipa{n1s1rB1n@} \\
 l.& \textipa{n-krm-n2} & \textipa{n1kr1mn@}, \textipa{n1k1rm1n@}  \\ 
 m.& \textipa{n-nk'm-n@}& \textipa{n1nk'1mn@} \\
 n.& \textipa{n-nfk-n@} & \textipa{n1nf1kn@} \\
 o.& \textipa{n-rmd-n@} & \textipa{n1rm1dn@} \\ 
 p.& \textipa{n-k'ff-n@} & \textipa{n1k'f1fn@} \\
 q.& \textipa{n-sdd-n@}  & \textipa{n1sd1dn@} \\ \hline
 \end{tabular}
\end{center}

@@

\begin{center} \renewcommand*\arraystretch{1.2}
\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c:c|} \hline 
\multicolumn{3}{|c||}{Input:~/\textipa{n-\textnormal{CCC}-n@}/} & {\sc Align-Left} & {\sc Anchor-Left Rt} \\[0.5ex]
\hline \hline a. & & \textipa{n1\textnormal{C.C}1\textnormal{C}.n@} & 2,3,5,6 & $\ast$! \\
\hline b. & \ding{43} & \textipa{n1.\textnormal{C}1\textnormal{C.C}1.n@} & 2,4!,5,7 & \\
\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
